### 2015-05-25 docs/report/inlining.tex
fixes inlining code sample from inlining report section.

  return (pixel & 0xFF000000) + (new_b << 16) + (new_g << 8) + (new_r & 0xFF);
}, function(result){
  // work on result
});
\end{lstlisting}

@@

  return (pixel & 0xFF000000) + (new_b << 16) + (new_g << 8) + (new_r & 0xFF);
}, function(result){
  // work on result
});
\end{lstlisting}

We created a benchmark to understand the difference between the initial version (the one in which functions were not inlined) and the final one (with inlining in charge of the developer):
\bmcode{http://jsperf.com/pjs-map-inlining/6}{../../spikes/3.1.3/pjsMapInlining/pjsMapInlining.js}

>>>>

  return (pixel & 0xFF000000) + (new_b << 16) + (new_g << 8) + (new_r & 0xFF);
}).seq(function(result){
  // work on result
});
\end{lstlisting}

@@

  return (pixel & 0xFF000000) + (new_b << 16) + (new_g << 8) + (new_r & 0xFF);
}).seq(function(result){
  // work on result
});
\end{lstlisting}

We created a benchmark to understand the difference between the initial version (the one in which functions were not inlined) and the final one (with inlining in charge of the developer):
\bmcode{http://jsperf.com/pjs-map-inlining/7}{../../spikes/3.1.3/pjsMapInlining/pjsMapInlining.js}
